---
title: "Demo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is a demo vignette for `simBA`.

```{r setup}
library(simBA)
```

First, a user can create the `parameters` object that will be supplied to `simBA()` containing the parameters for the simulation design.

```{r}
parameters <- create_parameters(nbinary = 6,
                                ncontinuous = 1,
                                ncount = 1,
                                # file = "parameters.csv",
                                unmeasured_conf = "u1",
                                unmeasured_type = "binary")

# Note: uncomment `file` argument to automatically save file to supplied path
```

The user can manually fill in the parameter values. An example file comes with the package, which we can load in using the following:

```{r}
parameters <- read.csv(system.file("extdata", "parameters.csv",
                                   package = "simBA"))
```

We can then run the simulation using `simBA()`:

```{r}
sim <- simBA(parameters,
             iterations = 200,
             size = 500,
             treatment_prevalence = .2,
             treatment_coeff = -.25,
             outcome_prevalence = .4,
             unmeasured_conf = "u1",
             n_proxies = 2,
             proxy_type = "binary",
             corr = .7,
             # cl = 4, #uncomment for speed on Mac
             verbose = FALSE)

sim
```

We can look at the results:

```{r}
summary(sim)

plot(sim, "balance")

plot(sim, "hr")
```

See `?plot.simBA` for details.